\documentclass{article}
\begin{document}
\author{Rhys}
\title{Meeting Minutes - 8th May 2007}
\maketitle
\begin{flushleft}
Attendees:
Mel (Chair),
Rhys (Sec),
Rob,
Joel,
Braden,
Brian
\newline

\begin{enumerate}
  \item Xilinx Board 
    \begin{itemize}
      \item Has arrived after being ordered.
      \item AI: Joel and Mel to commence testing
    \end{itemize}
  
  \item IRSIM status update (Rob)
    \begin{itemize}
      \item Almost entirely working
      \item There are still problems with membyteen though. Even with the
            clock speed slowed down really far, it still seems to be
            arriving at the wrong time. In the simulation of 'gold standard'
            verilog, it changes before ph1.
      \item We need to look at the desired behaviour of the memory interface,
            in particular membyteen. This might be in the book See MIPS Run,
            so endeavour to find a local copy.
      \item AI: Look at releveant documentation/specification (Rhys)
      \item AI: Move on to nanosim testing (Rob)
  \end{itemize}

  \item America Trip 
    \begin{itemize}
      \item Didn't hear back from Dean 
      \item Assume it will not happen 
  \end{itemize}

  \item Project Implimentation Plan feedback
    \begin{itemize}
      \item Dr Phillips should have given feedback prior to submission of
            critical design review.
  \end{itemize}

  \item Peer review
    \begin{itemize}
      \item Suggestion to cross review/look at each others peer reviews
  \end{itemize}

  \item Meeting documentation
    \begin{itemize}
      \item Braden emphasised the importance of the meeting documentation
            as an assesment tool.
      \item Joel is LaTexing the meeting documentation (agendas and minutes)
  \end{itemize}

\end{enumerate}

\end{flushleft}

\end{document}
