\documentclass{article}
\begin{document}
\author{Mel}
\title{Meeting Minutes - 27 March 2007}
\maketitle
\begin{flushleft}

Attendees
Joel (Chair)
Mel (Sec)
Rob
Rhys
Braden
\newline

\begin{enumerate}
  \item Prior Business
    \begin{itemize}
    \item AI: Joel - follow up on which FPGA board to purchace
    \item AI: Rhys - follow up on logo requrements of our chip.
                     use Xchiplogo program to generate our logo
    \end{itemize}

  \item Progress on the system level verification
    \begin{itemize}
    \item EDA tools (Rob) - Simulate Verilog on Cadence or Synopsis
    \item VCD parse (Joel) - Parse the Verilog command dump files (vcd) and
          convert to a form usable by IRSIM. Run the spec simulation and 
          generate VCD from that
    \item Verilog trace writes (Mel) - Braden briefly explained that trace
          writes in the Verilog file should produce a dump file which
          contains all inputs and outputs of the MIPS on different clock cycles.
    \item Snoopgen (Rhys) - Concept similar to Verilog trace writes but
          using snoopgen.
    \end{itemize}

  \item  Deadlines for the system level verification testing
    \begin{itemize}
    \item Deadline for the chip based on HMC milestone: 10th April 2007
    \item Joel suggested that team should send out status emails
          specifing progress on friday afternoon, and whomever
          had made the most progress will help other team members
          with their problems.
    \end{itemize}

  \item Next set of deliverables
    \begin{itemize}
    \item Reults from system level verifications
    \item Electrical tests
    \end{itemize}

  \item Supervisor feedback (proposal seminar)
    \begin{itemize}
    \item Assessment will be on the team and also on individual team members.
    \item Overall performance is good, outstanding team members are Joel
          and Rhys.
    \end{itemize}
  
  \item Actions
    \begin{itemize}
    \item Order FPGA board.
    \item Generate a chip logo for our team.
    \item Each member has to work out their individual part of the system
          level verification.
    \item Bring \$20 to the next meeting, deposit for borrowing stuff from
          the store.
    \end{itemize}

  \item Other business
    \begin{itemize}
    \item Braden mentioned that a copy of the Project Implimentation Plan
          should be included on the Project CD
    \end{itemize}
\end{enumerate}

\end{flushleft}

\end{document}
